### 2024-05-18 fantasy-football.qmd
20240518 - edits

A fantasy football "league" is composed of various imaginary (i.e., "fantasy") teams—and their associated manager.
In the fantasy league, the managers' fantasy teams play against each other.
A fantasy league is commonly composed of 8 or 10 fantasy teams, but leagues can have more or fewer teams.

@@

On a given roster, a manager has a "starting lineup" and a "bench".
Each week, the manager decides which players on their roster to put in the starting lineup, and which to keep on the bench.
In many leagues, a starting lineup is composed of one or more spots for each of the following:

@@

- Quarterback (QB)
- Running Back (RB)
- Wide Receiver (WR)
- Tight End (TE)
- Flex Position—a flexible position that can involve a player from various positions: e.g., a RB or WR or TE

@@

- Kicker (K)

@@

- Team Defense (DST/D/DEF) or Individual Defensive Player (IDP)

>>>>

A fantasy football "league" is composed of various imaginary (i.e., "fantasy") teams—and their associated manager.
In the fantasy league, the managers' fantasy teams play against each other.
A fantasy league is commonly composed of 8, 10, or 12 fantasy teams, but leagues can have more or fewer teams.

@@

On a given roster, a manager has a "starting lineup" and a "bench".
Each week, the manager decides which players on their roster to put in the starting lineup, and which to keep on the bench.
In many leagues, a starting lineup is composed of offensive players, a kicker, and defense/special teams:

@@

| Position           | Typical Number of Players in Starting Lineup |
|--------------------|----------------------------------------------|
| Quarterback (QB)   | 1                                            |
| Running Back (RB)  | 2                                            |
| Wide Receiver (WR) | 2                                            |
| Tight End (TE)     | 1                                            |
| Flex Position      | 1                                            |

A "flex position" is a flexible position that can involve a player from various positions: e.g., a RB or WR or TE.

@@

- one Kicker (K)

@@

- one Team Defense (DST/D/DEF) or multiple Individual Defensive Players (IDP)
